Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added README.txt, which illustrates our figures were made by Ipe

After carrying out the dilation-erosion-dilation-based method, 
we simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$.
If two buffers overlap, 
then the original buildings are put in the same group.

%(see \fig\ref{fig:RemoveBay} for example).
As stated in \sect\ref{sec:Simplify}, 
we wish to remove ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may come from a complex original building,
or from bridging some buildings.
\fig\ref{fig:RemoveBay}e shows an example of the latter case.
To remove a bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
For the buildings in \fig\ref{fig:RemoveBay}a,
the final result of removing a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

Definition of $\dtrm{C}$

@@

>>>>

After carrying out the dilation-erosion-dilation method, 
we simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$.
We will talk about how to define $\dtrm{C}$ later.
If two buffers overlap, 
then the original buildings are put in the same group.

%(see \fig\ref{fig:RemoveBay} for example).
As stated in \sect\ref{sec:Simplify}, 
we wish to remove ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may come from a complex original building,
or from bridging some buildings.
\fig\ref{fig:RemoveBay}e shows an example of the later case.
To remove a bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
For the buildings in \fig\ref{fig:RemoveBay}a,
the final result of removing a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

The prob
Definition of $\dtrm{C}$

@@

Following \citet{Stoter2009} and Following \citet{Chaudhry2008}, 
we set
